Why is it that statistical tests for residuals are not widely used? An explanation using visual inference.

### 2023-02-14 paper_comparison/paper_comparison/paper_comparison.Rmd
update the power desc

```{=tex}
\begin{equation} \label{eq:logistic-regression-1-1}
Pr(\text{reject}~H_0|H_1,E) = \Lambda(log(\frac{0.05}{0.95}) + \beta_1 E),
\end{equation}
```
\noindent where $\Lambda(.)$ is the standard logistic function given as $\Lambda(z) = exp(z)/(1+exp(z))$. The effect size is the only regressor and the intercept is fixed to $log(0.5/0.95)$ so that $\hat{Pr}(\text{reject}~H_0|H_1,E = 0) = 0.05$.

Effect size $E$ is derived from the Kullback-Leibler divergence (see Appendix for the details) formulated as

@@

\begin{gather}  \label{eq:effect-size}
E = \frac{1}{2}\left(log\frac{|diag(\boldsymbol{R}_a\boldsymbol{V})|}{|diag(\boldsymbol{R}_a\sigma^2)|} - n + tr(diag(\boldsymbol{R}_a\boldsymbol{V})^{-1}diag(\boldsymbol{R}_a\sigma^2)) + \boldsymbol{\mu}_z^{T}(\boldsymbol{R}_a\boldsymbol{V})^{-1}\boldsymbol{\mu}_z\right),\\
\boldsymbol{R}_a = \boldsymbol{I}_n - \boldsymbol{H}_a,\\
\boldsymbol{H}_a = \boldsymbol{X}_a(\boldsymbol{X}_a^T\boldsymbol{X}_a)^{-1}\boldsymbol{X}_a^T,
\end{gather}

@@

\noindent where $diag(.)$ is the diagonal matrix constructed from the diagonal elements of a matrix,  $\boldsymbol{X}_a = (\boldsymbol{1},  \boldsymbol{X})$ is the matrix of regressors including the intercept used in the regression equation, $\sigma^2\boldsymbol{I}$ is the assumed variance of the error term when $H_0$ is true, $\boldsymbol{V}$ is the actual variance of the error term, and $\boldsymbol{\mu}_z = \boldsymbol{R}_a\boldsymbol{Z}\boldsymbol{\beta}_z$ is the expected values of the residuals with $\boldsymbol{Z}$ be any variables leave out by the model and $\boldsymbol{\beta}_z$ be the corresponding coefficients.

>>>>

```{=tex}
\begin{equation} \label{eq:logistic-regression-1-1}
Pr(\text{reject}~H_0|H_1,E) = \Lambda\left(log\left(\frac{0.05}{0.95}\right) + \beta_1 E\right),
\end{equation}
```
\noindent where $\Lambda(.)$ is the standard logistic function given as $\Lambda(z) = exp(z)/(1+exp(z))$. The effect size is the only regressor and the intercept is fixed to $log(0.05/0.95)$ so that $\hat{Pr}(\text{reject}~H_0|H_1,E = 0) = 0.05$.

Effect size $E$ is formulated as the conditional expectation of the sample-based effect size $E_{sample}$ derived from the Kullback-Leibler divergence (see Appendix for the details) given by

@@

\begin{gather}  \label{eq:effect-size}
E = E[E_{sample}|M],\\
E_{sample} = \frac{1}{2}\left(log\frac{|diag(\boldsymbol{R}_a\boldsymbol{V})|}{|diag(\boldsymbol{R}_a\sigma^2)|} - n + tr(diag(\boldsymbol{R}_a\boldsymbol{V})^{-1}diag(\boldsymbol{R}_a\sigma^2)) + \boldsymbol{\mu}_z^{T}(\boldsymbol{R}_a\boldsymbol{V})^{-1}\boldsymbol{\mu}_z\right),\\
\boldsymbol{R}_a = \boldsymbol{I}_n - \boldsymbol{H}_a,\\
\boldsymbol{H}_a = \boldsymbol{X}_a(\boldsymbol{X}_a^T\boldsymbol{X}_a)^{-1}\boldsymbol{X}_a^T,
\end{gather}

@@

\noindent where $M$ is a given model that generates the data, $diag(.)$ is the diagonal matrix constructed from the diagonal elements of a matrix,  $\boldsymbol{X}_a = (\boldsymbol{1},  \boldsymbol{X})$ is the matrix of regressors including the intercept used in the regression equation, $\sigma^2\boldsymbol{I}$ is the assumed variance of the error term when $H_0$ is true, $\boldsymbol{V}$ is the actual variance of the error term, and $\boldsymbol{\mu}_z = \boldsymbol{R}_a\boldsymbol{Z}\boldsymbol{\beta}_z$ is the expected values of the residuals with $\boldsymbol{Z}$ be any variables leave out by the regression equation and $\boldsymbol{\beta}_z$ be the corresponding coefficients. An expectation is taken because $E_{sample}$ depends on the regressors $X$ and we want the effect size $E$ to be the same for the same data generating process. It is difficult to solve the effect size $E$ analytically, so we estimate it with the average of $E_{sample}$ over a very large sample size.

### 2023-02-14 paper_comparison/paper_comparison/paper_comparison.tex
update the compiled paper
update the power desc

@@

\begin{equation} \label{eq:logistic-regression-1-1}
Pr(\text{reject}~H_0|H_1,E) = \Lambda(log(\frac{0.5}{0.95}) + \beta_1 E),
\end{equation}

\noindent where \(\Lambda(.)\) is the standard logistic function given
as \(\Lambda(z) = exp(z)/(1+exp(z))\). The effect size is the only
regressor and the intercept is fixed to \(log(0.5/0.95)\) so that
\(\hat{Pr}(\text{reject}~H_0|H_1,E = 0) = 0.05\).

Effect size \(E\) is derived from the Kullback-Leibler divergence (see
Appendix for the details) formulated as

@@

\noindent where \(diag(.)\) is the diagonal matrix constructed from the
diagonal elements of a matrix,
\(\boldsymbol{X}_a = (\boldsymbol{1}, \boldsymbol{X})\) is the matrix of
regressors including the intercept used in the regression equation,
\(\sigma^2\boldsymbol{I}\) is the assumed variance of the error term
when \(H_0\) is true, \(\boldsymbol{V}\) is the actual variance of the
error term, and
\(\boldsymbol{\mu}_z = \boldsymbol{R}_a\boldsymbol{Z}\boldsymbol{\beta}_z\)
is the expected values of the residuals with \(\boldsymbol{Z}\) be any
variables leave out by the model and \(\boldsymbol{\beta}_z\) be the
corresponding coefficients.

>>>>

(use uniform effect size? normal effect size? -\textgreater{} other
dist?)

(average out dist for effect size calc?)

@@

\begin{equation} \label{eq:logistic-regression-1-1}
Pr(\text{reject}~H_0|H_1,E) = \Lambda\left(log\left(\frac{0.05}{0.95}\right) + \beta_1 E\right),
\end{equation}

\noindent where \(\Lambda(.)\) is the standard logistic function given
as \(\Lambda(z) = exp(z)/(1+exp(z))\). The effect size is the only
regressor and the intercept is fixed to \(log(0.05/0.95)\) so that
\(\hat{Pr}(\text{reject}~H_0|H_1,E = 0) = 0.05\).

Effect size \(E\) is formulated as the conditional expectation of the
sample-based effect size \(E_{sample}\) derived from the
Kullback-Leibler divergence (see Appendix for the details) given by

@@

\noindent where \(M\) is a given model that generates the data,
\(diag(.)\) is the diagonal matrix constructed from the diagonal
elements of a matrix,
\(\boldsymbol{X}_a = (\boldsymbol{1}, \boldsymbol{X})\) is the matrix of
regressors including the intercept used in the regression equation,
\(\sigma^2\boldsymbol{I}\) is the assumed variance of the error term
when \(H_0\) is true, \(\boldsymbol{V}\) is the actual variance of the
error term, and
\(\boldsymbol{\mu}_z = \boldsymbol{R}_a\boldsymbol{Z}\boldsymbol{\beta}_z\)
is the expected values of the residuals with \(\boldsymbol{Z}\) be any
variables leave out by the regression equation and
\(\boldsymbol{\beta}_z\) be the corresponding coefficients. An
expectation is taken because \(E_{sample}\) depends on the regressors
\(X\) and we want the effect size \(E\) to be the same for the same data
generating process. It is difficult to solve the effect size \(E\)
analytically, so in the analysis, we estimate it with the average of
\(E_{sample}\) over a very large sample size.
